\textbf{AprilTrack: A Particle-Filter based AprilTag Tracker}

### 2017-01-14 paper/paper.tex
Worked on paper a bit

	The AprilTrack algorithm proposed in this paper seeks to bridge two existing fields of research in computer vision literature: fiducial detection and monocular object tracking. With a rise in the popularity of fiducials, or artificial markers, as a source of ground-truth position data for mobile robots, there has been a considerable interest in designing robust and blur-resistant fiducials. Rather than devising a new fiducial, This paper attempts to improve on existing fiducials such as the popular AprilTag marker by augmenting fiducial detection algorithms with a particle-filter based monocular object tracker which reliably tracks a fiducial's position and orientation in six degrees of freedom, allowing for tag-based localization in situations where still frame based methods would be unable to do so. This novel particle-filter based algorithm is evaluated on several datasets involving both ego-motion and tag-based-motion and is compared to standalone tag detection algorithms and ground-truth tag position data.

@@

where $\vec{r}$ is the three dimensional position of the tracked object, $\dot{\vec{q}}$ is the three dimensional velocity, $\vec{q}$ is a four dimensional unit quaternion containing the pose of the tracked object, and $\vec{\omega}$ is an angular velocity with components $\omega_x$, $\omega_y$, and $\omega_z$. We use $\vec{y}_k$ to denote the measurement (appearance) of the tag a particular time $t$.

@@

After selecting the particle with the highest weight as the most likely candidate, the final resampling step simply consists of drawing a new set of $N$ particles with equal weights (normalized to one) from the distribution $p(\vec{x}_t|\vec{y}_{1:t})$ where $p(\vec{x}_t|\vec{y}_{1:t})$ is approximated by the set of weighted particles.

@@

@@

\begin{figure}[b]
	\centering
	\includegraphics[width=7.5cm,height=5cm]{Particles2}
	\caption{The distribution of particles and their weights with respect to the X,Y position of the particles.}
\end{figure}

\begin{figure}[b]
	\centering
	\includegraphics[width=7.5cm,height=5cm]{RefPatches}
	\caption{The reference patches of various tags (by ID) in a multi-Tag tracking scenario.}
\end{figure}

>>>>

	The AprilTrack algorithm proposed in this paper seeks to bridge two existing fields of research in computer vision literature: fiducial detection and monocular object tracking. With a rise in the popularity of fiducials, or artificial markers, as a source of ground-truth position data for mobile robots, there has been considerable interest in designing robust and blur-resistant fiducials. Rather than devising a new fiducial, this paper attempts to improve on existing fiducials such as the popular AprilTag marker by augmenting fiducial detection algorithms with a particle-filter based monocular object tracker which reliably tracks a fiducial's position and orientation in six degrees of freedom, allowing for tag-based localization in situations where still frame based methods would be unable to do so. This novel particle-filter based algorithm is evaluated on several datasets involving both ego-motion and tag-based-motion and is compared to ground-truth tag position data.

@@

where $\vec{r}$ is the three dimensional position of the tracked object, $\dot{\vec{q}}$ is the three dimensional velocity, $\vec{q}$ is a four dimensional unit quaternion containing the pose of the tracked object, and $\vec{\omega}$ is an angular velocity with components $\omega_x$, $\omega_y$, and $\omega_z$. We use $\vec{z}_k$ to denote the measurement (appearance) of the tag a particular time $t$.

@@

After selecting the particle with the highest weight as the most likely candidate, the final resampling step simply consists of drawing a new set of $N$ particles with equal weights (normalized to one) from the distribution $p(\vec{x}_t|\vec{z}_{1:t})$ where $p(\vec{x}_t|\vec{z}_{1:t})$ is approximated by the set of weighted particles.

@@

\begin{figure}[b]
	\centering
	\includegraphics[width=7cm,height=4.75cm]{Particles2}
	\caption{The distribution of particles and their weights with respect to the X,Y position of the particles.}
\end{figure}

\begin{figure}[b]
	\centering
	\includegraphics[width=7cm,height=4.75cm]{RefPatches}
	\caption{The reference patches of various tags (by ID) in a multi-Tag tracking scenario.}
\end{figure}

@@
